\chapter{Control Plane Saturation Attack and Countermeasures in Software
defined Networking}

\section{Concept}
We tipical have \textbf{Data Plane} that decides what to do with packetss coming
from an interface. It makes use of routing and forwarding tables.
There are \textbf{Control Plane} that esablishes the state in routers.

This devices are specialized, and there is lack of abstraction on the Control
Plane.

\subsection{Software Defined Networking}
Thee idea behind SDN is to have some software abstraction, with differente
control plane in the same hardware.
The idea is to take the Control Plane away from the hardware and to move it in
the "software" layer.

\subsubsection{OpenFlow}
\begin{itemize}
  \item Key enabler for SDN
  \item Communication protocol between Data Plane and Control Plane
  \item Routing is based on network flows (TCP + IP + port + etc)
  \item Flow rules are dictated by the Controller
  \item Controller can collect statistics from switches
  \item Controller can install new flow rules:
  \begin{itemize}
    \item Proactively (pre-install rules)
    \item Reactively ("on-demand"). Issues related:
    \begin{itemize}
      \item Scalability: Every "unknow" flow is forwarded to the Control
Plane: Possible Control Plane saturation attack (lile DoS)
      \item Responsiveness
    \end{itemize}
  \end{itemize}
\end{itemize}

\paragraph*{Control Plane Saturation attack}
\begin{itemize}
  \item Aims at incapacitating the Control Plane
  \item Forces a target switch to flood the Control Plane with
\textbf{PACKET\_IN} requests, generating requests for unknow flows.
  \item Particularly strong using \textbf{SYN} Flooding. This are difficult to
detect, and the target is the controller: non end-to-end countermeasures can be
used.
\end{itemize}
The solution is using \textbf{Avant Guard}, that handle in a better way the
\textbf{SYN} request. But there are problems also with this solutions. So
another way to solve the problem is using \textbf{LineSwitch}.
The Goal of LineSwith is to reduce the need for proxy, and the idea is to proxy
with some probability $P_P$, and count every time we were unable to proxy the
traffic per IP.
